---
title: "fulltext Vignette: Additional Publishers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fulltext Vignette: Additional Publishers}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## About the package

`fulltext` is an R package to search for articles, download those articles in full text if available, convert pdf format to plain text, and extract text chunks for vizualization/analysis.

* Plos
* Crossref
* BioRxiv
* Entrez
* arXiv
* BMC
* Europe PMC
* Scopus

Please get your own API keys for each of the different .

I set up the functions so that you can put the key in your `.Renviron` file, which will be called on startup of R, and then you don't have to enter your API key for each run of a function. Add entries for an R session like

```
Sys.setenv(SCOPUS_API_KEY = "YOURKEYHERE")
Sys.setenv(BMC_API_KEY = "YOURKEYHERE")
Sys.setenv(MICROSOFT_API_KEY = "YOURKEYHERE")
```

Or set them across sessions by putting entries in your `.Renviron` file like

```
SCOPUS_API_KEY=<yourkey>
BMC_API_KEY=<yourkey>
MICROSOFT_API_KEY=<yourkey>
```

You can also pass in your key in a function call, but be careful not to expose your keys in code committed to public repositories. If you do pass in a function call, use e.g., `Sys.getenv("SCOPUS_API_KEY")`.

## Install fulltime

From CRAN


```r
install.packages("fulltext")
```

Development version from GitHub


```r
install.packages("devtools")
devtools::install_github("ropensci/fulltext")
```

## Load fulltext


```{r}
library('fulltext')
```

## Search on Scopus

After registering for an API key from Scopus, use the commandabove to add the api key tothe environment variable `SCOPUS_API_KEY`. The code below will search for papers on `air quality monitoring` on Scopus.

```{r,eval=FALSE}
res1 <- ft_search(query = 'air quality monitoring', from = 'scopus',scopusopts = list(key=Sys.getenv("SCOPUS_API_KEY")))
```

```{r,eval=FALSE}
res1$scopus
Query: [air quality monitoring] 
Records found, returned: [172256, 10] 
 
                                                         prism:url         dc:identifier
1  https://api.elsevier.com/content/abstract/scopus_id/85054195467 SCOPUS_ID:85054195467
2  https://api.elsevier.com/content/abstract/scopus_id/85053839201 SCOPUS_ID:85053839201
3  https://api.elsevier.com/content/abstract/scopus_id/85051920458 SCOPUS_ID:85051920458
4  https://api.elsevier.com/content/abstract/scopus_id/85053052770 SCOPUS_ID:85053052770
5  https://api.elsevier.com/content/abstract/scopus_id/85053790411 SCOPUS_ID:85053790411
6  https://api.elsevier.com/content/abstract/scopus_id/85047169794 SCOPUS_ID:85047169794
7  https://api.elsevier.com/content/abstract/scopus_id/85053799252 SCOPUS_ID:85053799252
8  https://api.elsevier.com/content/abstract/scopus_id/85053340640 SCOPUS_ID:85053340640
9  https://api.elsevier.com/content/abstract/scopus_id/85053788265 SCOPUS_ID:85053788265
10 https://api.elsevier.com/content/abstract/scopus_id/85053815780 SCOPUS_ID:85053815780
Variables not shown: eid (chr), dc:title (chr), dc:creator (chr), prism:publicationName
     (chr), prism:issn (chr), prism:volume (chr), prism:pageRange (chr), prism:coverDate
     (chr), prism:coverDisplayDate (chr), prism:doi (chr), pii (chr), citedby-count
     (chr), affiliation (list), prism:aggregationType (chr), subtype (chr),
     subtypeDescription (chr), source-id (chr), openaccess (chr), openaccessFlag (lgl),
     prism:eIssn (chr), prism:issueIdentifier (chr), article-number (chr)
```

## Search using arXiv

The code below will search for papers on `air quality monitoring` on arXiv repository. For arXiv, an api is not required.

```{r,eval=FALSE}
res_arXiv$arxiv
Query: [air quality monitoring] 
Records found, returned: [44988, 10] 
License: [variable, but should be free to text-mine, see http://arxiv.org/help/license and http://arxiv.org/help/bulk_data] 
                   id           submitted             updated
1    hep-th/9110066v1 1991-10-24 19:33:53 1991-10-24 19:33:53
2  cond-mat/9208006v1 1992-08-11 15:29:45 1992-08-11 15:29:45
3  astro-ph/9208005v1 1992-08-25 06:45:03 1992-08-25 06:45:03
4   hep-lat/9209009v1 1992-09-04 18:35:35 1992-09-04 18:35:35
5    hep-ph/9209236v1 1992-09-15 14:58:00 1992-09-15 14:58:00
6   hep-lat/9209022v1 1992-09-22 17:05:11 1992-09-22 17:05:11
7  astro-ph/9211002v1 1992-11-04 12:59:22 1992-11-04 12:59:22
8    hep-ph/9212312v2 1992-12-28 17:16:34 1993-02-01 16:45:39
9    hep-ph/9301239v1 1993-01-14 09:47:00 1993-01-14 09:47:00
10 astro-ph/9301008v1 1993-01-15 15:37:30 1993-01-15 15:37:30
Variables not shown: title (chr), abstract (chr), authors (chr), affiliations (chr),
     link_abstract (chr), link_pdf (chr), link_doi (chr), comment (chr), journal_ref
     (chr), doi (chr), primary_category (chr), categories (chr)
```
